Investigating soundscapes perception through acoustic scenes simulation.

### 2017-08-24 lafaySimulatedScenePerception.tex
fixed figure layout

\documentclass[preprint,12pt]{elsarticle}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{caption}
\usepackage{sectsty}
\usepackage{amsmath}
\usepackage{color}

@@

\journal{Nuclear Physics}

@@

\ml{fix trim and check why figures goes offline}

\begin{figure}[t]
        \myfloatalign
        \includegraphics[trim={5cm 0 0 0},clip,width=.8\linewidth]{gfx/ch_4/3.png}
       \caption{Hierarchical organisation of the isolated sounds used in the simulation.}\label{fig:orgDb}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.8\columnwidth]{gfx/ch_4/SSF}\label{fig:ssf}} \par
        \subfloat[]
        {\includegraphics[width=\columnwidth]{gfx/ch_4/simscene}\label{fig:simscene}}
       \caption{Graphical interfaces for the selection of sound classes (a) and their sequencing (b) of the \emph{simScene} tool.}
\end{figure}

@@

\begin{figure}[t]
        \myfloatalign
        \includegraphics[width=\linewidth]{gfx/ch_5/5.png}
        \caption{Experimental protocol of the simulation experiment (1.a) and the pleasantness evaluation experiment (1.b)}\label{fig:xp1_2}
\end{figure}

@@

\begin{figure*}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_1}\label{fig:soundlevela}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_3}\label{fig:soundlevelb}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_5}\label{fig:soundlevelc}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_2}\label{fig:soundleveld}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_4}\label{fig:soundlevele}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_6}\label{fig:soundlevelf}}
       \caption{Distributions of the structural features $L$ (a, d), $L(E)$ (b, e) et $L(T)$ (c, f), with respect to scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiments 1.b (d, e, f).}
\end{figure*}

@@

\begin{figure}[t]
        \myfloatalign
        \subfloat[]
        {\includegraphics[width=1\linewidth]{gfx/ch_5/xp1_class_1}\label{fig:soundsourcea}} \par
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_2}\label{fig:soundsourceb}}
        \subfloat[]
        {\includegraphics[width=.4\linewidth]{gfx/ch_5/xp1_class_3}\label{fig:soundsourcec}}
       \caption{Proportion of synthesized scenes (i or ni) involving a specific class of sounds: (a) event classes at an abstraction level $0+$, (b) texture classes at an abstraction level $0$, (c) event sub-classes at an abstraction level $1$ belonging to \emph{traffic} and \emph{public transportation} classes of the abstraction level $0$.}\label{fig:soundsource}
\end{figure}

>>>>

\documentclass[12pt]{elsarticle}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{caption}
\usepackage{sectsty}
\usepackage{amsmath}
\usepackage{color}

@@

\journal{Behavior Research Methods}

@@

\begin{figure}
        \myfloatalign
        \includegraphics[trim={0 0 0 2.5cm},clip,width=.8\linewidth]{gfx/ch_4/3.png}
       \caption{Hierarchical organisation of the isolated sounds used in the simulation.}\label{fig:orgDb}
\end{figure}

@@

\begin{figure}
        \subfloat[]
        {\includegraphics[width=.8\linewidth]{gfx/ch_4/SSF}\label{fig:ssf}} \par
        \subfloat[]
        {\includegraphics[width=\linewidth]{gfx/ch_4/simscene}\label{fig:simscene}}
       \caption{Graphical interfaces for the selection of sound classes (a) and their sequencing (b) of the \emph{simScene} tool.}
\end{figure}

@@

\begin{figure}
        \includegraphics[width=\linewidth]{gfx/ch_5/5.png}
        \caption{Experimental protocol of the simulation experiment (1.a) and the pleasantness evaluation experiment (1.b)}\label{fig:xp1_2}
\end{figure}

@@

\begin{figure*}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_1}\label{fig:soundlevela}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_3}\label{fig:soundlevelb}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_5}\label{fig:soundlevelc}}\par
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_2}\label{fig:soundleveld}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_4}\label{fig:soundlevele}}
        \subfloat[]
        {\includegraphics[width=.33\linewidth]{gfx/ch_5/xp_soundlevel_6}\label{fig:soundlevelf}}
       \caption{Distributions of the structural features $L$ (a, d), $L(E)$ (b, e) et $L(T)$ (c, f), with respect to scene type (a, b, c) and perceived pleasantness $\mathcal{A}_{scene}$ of experiments 1.b (d, e, f).}
\end{figure*}

@@

\begin{figure}
        \subfloat[]
        {\includegraphics[width=1\linewidth]{gfx/ch_5/xp1_class_1}\label{fig:soundsourcea}} \par
        \subfloat[]
        {\includegraphics[width=.5\linewidth]{gfx/ch_5/xp1_class_2}\label{fig:soundsourceb}}
        \subfloat[]
        {\includegraphics[width=.5\linewidth]{gfx/ch_5/xp1_class_3}\label{fig:soundsourcec}}
       \caption{Proportion of synthesized scenes (i or ni) involving a specific class of sounds: (a) event classes at an abstraction level $0+$, (b) texture classes at an abstraction level $0$, (c) event sub-classes at an abstraction level $1$ belonging to \emph{traffic} and \emph{public transportation} classes of the abstraction level $0$.}\label{fig:soundsource}
\end{figure}
